---
title: "cachematrix.rmd"
author: "LEF"
date: "December 26, 2015"
output: pdf_document
---
## Introduction
cachematrix.R is my attempt at completing programming assignment 2 for the Coursera ['R Programming'](https://class.coursera.org/rprog-035) course, December 2015. Instead of using 'solve' to take the inverse, I am using 'ginv' from the MASS library (see References). This increases the difficulty in running the code, as you must have access to the MASS library, but ginv handles non-square matrices.

## Example
The functions inside take the inverse of a matrix and store it for later re-use. First, generate a matrix, and create a list of functions for manipulating it.
```{r}
source('cachematrix.R')
rmat = matrix(runif(1000000), nrow=1000, ncol=1000)
a <- makeCacheMatrix(rmat)
```

Next, compute the matrix inverse. Repeated calls will not re-compute, but will instead use the cached result. 

```{r}
system.time(inv <- cacheSolve(a))
system.time(inv <- cacheSolve(a))
```

Note the difference in run time between computing and returning the cached version.

## References
Venables, W. N. & Ripley, B. D. (2002) Modern Applied Statistics with S. Fourth Edition. Springer, New York. ISBN 0-387-95457-0 